Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics

### 2020-04-20 Paper/main.tex
Edited plot formatting and deleted unnecessary comments

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
% Provide a summary of the session. What was done, what measurements were taken,
% brief methods, what calculations, brief conclusion.  The Abstract should be
% approximately 250 words or fewer, italicized, in 10-point Times (or Times
% Roman.) Please leave two spaces between the Abstract and the heading of your
% first section.  It should briefly summarize the essence of the paper and address
% the following areas without using specific subsection titles. Objective: Briefly
% state the problem or issue addressed, in language accessible to a general
% scientific audience. Technology or Method: Briefly summarize the technological
% innovation or method used to address the problem. Results: Provide a brief
% summary of the results and findings. Conclusions: Give brief concluding remarks
% on your outcomes. Detailed discussion of these aspects should be provided in the
% main body of the paper.
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation. The random
  walk consists of a walker making steps in random directions, with each step
  having a probability of causing the walker to die and the random walk to end,
  with the probability determined by a function of position. The function can be
  chosen to model specific quantum systems. The rate of death of the walkers is
  used to calculate the ground state energy.

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/multiplot1.pdf}
    \caption{Histogram plotted on a logarithmic scale showing the Probability of
      surviving to at least a particular step in different infinite square wells
      with different boundaries $J$. The simulations were run with $10000$
      walkers The $\lambda J^2$ values for each are shown. The values get closer
      to the theoretical value of $\frac{\pi^2}{8} = 1.2337$ as we increase the
      size of the well. This is likely due to more walkers surviving to a higher
      number of steps, as the well size is increased.}
    \label{fig:multi_line_plot}
  \end{center}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation. The random
  walk consists of a walker making steps in random directions, with each step
  having a probability of causing the walker to die and the random walk to end,
  with the probability determined by a function of position. The function can be
  chosen to model specific quantum systems. The rate of death of the walkers is
  used to calculate the ground state energy.

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/multiplot.pdf}
    \caption{Histogram plotted on a logarithmic scale showing the Probability of
      surviving to at least a particular step in different infinite square wells
      with different boundaries $J$. The simulations were run with $10000$
      walkers The $\lambda J^2$ values for each are shown. The values get closer
      to the theoretical value of $\frac{\pi^2}{8} = 1.2337$ as we increase the
      size of the well. This is likely due to more walkers surviving to a higher
      number of steps, as the well size is increased.}
    \label{fig:multi_line_plot}
  \end{center}
\end{figure}
